%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{sorinresume}

% For mathematical symbols
\usepackage{amsmath}
\usepackage{hyperref}

% Set applicant's personal data for header
\name{Roman Sorin}
\address{\href{https://github.com/romansorin}{github.com/romansorin}}
\contacts{(216) 302-8812 \linebreak roman@romansorin.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Developer}{Vesst}{Dec 2019 - Present}
			\begin{itemize}
				\item Structured full design and API systems with high-scalability and performance in mind; refactored APIs, schemas, and models across several projects improving maintainability of code and reducing the frequency of bugs experienced.
				\item Integrated caching of requests and queries made by services for reduced wait times and faster client-side performance.
				\item Solved obscure issues and downtime related to database and web server setup, preventing further downtime and loss; managed several large-scale projects simultaneously.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer}{Lexxify}{Feb 2020 - Nov 2020}	
			\begin{itemize}
				\item Redesigned the entire application ranging from infrastructure to actual implementation for a more efficient, high-quality product and user experience.
				\item Established internal documentation and practices to reduce overhead and improve developer experience.
				\item Built utilities and APIs to be used for internal and external consumption providing more consistency in responses, behavior, and ease of use.
				\item Incorporated project management techniques to maintain constant growth, increase frequency of updates, and ensure that there was constant collaboration across the team.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer}{Lets-go.design}{Jul 2019 - Dec 2019}		
			\begin{itemize}
				\item Added and maintained new features to both the admin and user-facing parts of the application, increasing exposure and adoption of the product.
				\item Obtained knowledge and guidance on best practices and asynchronous collaboration, resulting in a greater focus on quality through documentation and code review.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer}{CarbonWebPrint}{Jan 2019 - Jul 2019}
			\begin{itemize}
				\item Built a reporting dashboard for clients to view analytics resulting in increased profits and client retention.
				\item Furthered collaboration skills through the instruction of colleagues and pushed for changes in architecture, translating into more clients and projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{Layout Hierarchy and UX}{}{}
			\begin{itemize}
				\item Developed a comprehensive Python application which implemented AWS Alexa APIs, scraped pages, and performed image manipulation using OpenCV to standardize results and maintain constant features.
				\item Implemented a clustering algorithm to determine commonalities in most popular global website layouts, and designed several layout variants based on clustering results.
				\item Built a web app to randomly display a variant to a user and record their behavior; analyzed user behavior by looking at various metrics and patterns associated with layouts.
				\item Wrote an extensive research paper detailing the process, results, and implications, as well as possibilities for future research and real-world implementation.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{BoardVitals QA}{}{}	
			\begin{itemize}
				\item Reverse-engineered API requests to automatically query and parse exam questions/answers from a bank based on exam ID and authentication cookies. Manipulated API responses to display data concisely using JSON, implemented basic throttling to reduce the frequency of requests.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Skills}
		\begin{cvsubsection}{}{}{}	
			(\textit{proficient}): PHP, Laravel, JavaScript, HTML/CSS, React, Vue, Git (\textit{familiar}): SQL, Python, Unix, AWS
		\end{cvsubsection}
	\end{cvsection}
\end{document}
